---
title: "2022 Monitoring Plan"
author: "Emma Jones"
date: "6/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# built in R 3.6.2
library(tidyverse)
library(sf)
library(config)
library(DBI)
library(pool)
library(dbplyr)
library(leaflet)
library(inlmisc)
library(DT)
library(lubridate)
library(readxl)

# Get configuration settings
conn <- config::get("connectionSettings")

board_register_rsconnect(key = conn$CONNECT_API_KEY,  #Sys.getenv("CONNECT_API_KEY"),
                         server = conn$CONNECT_SERVER)#Sys.getenv("CONNECT_SERVER"))

## Connect to ODS production
pool <- dbPool(
  drv = odbc::odbc(),
  Driver = "ODBC Driver 11 for SQL Server",#Driver = "SQL Server Native Client 11.0",
  Server= "DEQ-SQLODS-PROD,50000",
  dbname = "ODS",
  trusted_connection = "yes"
)
```

## Project Background

BRRO's monitoring planning process is being updated to a more reproducible and efficient collaborative process that utilizes modern project sharing techniques. This report serves as one project archive to aid in future monitoring plan development.

The general steps of a monitoring plan development involve identifying where previous plans have sampled and what frequency, comparing that information with longer term sampling goals, and identifying stations to be monitored in the upcoming year. After the plan is mapped out for the forthcoming season, new stations are created (as needed) in CEDS, monitoring staff build runs to efficiently collect samples and program these runs in CEDS. After a region is done with their monitoring plan, Central Office staff review the plan to ensure statewide goals and budget are met, providing feedback for the region if needed.

### Data Gathering

First, we will bring in the 2022 IR dataset to get a longer term view of sampling efforts in BRRO. This dataset encompasses 2015-2020. The station project codes and sample frequency are useful to the planning process to ensure sampling goals have been met. 

After this data is summarized, we will pull the 2021 sample information (to date) from CEDS to run through a similar process. 

By mapping this information we can quickly identify areas that might be lacking data for upcoming assessment windows and correct for potential data gaps.

```{r conventionals IR2022}

```

