---
title: "wqm_sampling_param_tool"
author: "kb"
date: '2022-07-12'
output: html_document
---

*built as part of Emma's wqm_samplingntwktool --> for 2023 Rproj
*requires connection to data OR local files of BRRO conventionals, BRROregionInfo

We want to know
1) where do we have NO data?
2) where do we have missing data

this script
- ignores spg code QA -- filter out at the joining of the 2 datasets
- summarizes total visits per year, counts parameter-specific measurements
- summarizes those counts by year/IR window and station, gives percentage of total visits by param counts!
- creates a new df for whittling down all that info into just seeing sample counts by IR window AND param percent reporting for each window (i.e., if "IR26Temp" value for a station is 100, that means you've got temperature measurements for every sample visit, if it's 50 you're missing half and so on)

```{r}
#count_na <- function(x) sum(is.na(x))

BRROregionInfo <- readRDS(paste0('data/BRROregionInfo.RDS'))
BRROconventionals <- readRDS(paste0('../for2022/data/IR2022conventionalsBRRO.RDS')  ) %>% 
  rename(FDT_TEMP_CELCIUS =`TEMPERATURE_00010_DEGREES CENTIGRADE` ,
         FDT_FIELD_PH= pH_00400_STD_UNITS ,
         DO_mg_L= `DO_mg/L`)

#a big big table of sample n's and param NAs by IR window
ParamSampleInfo <- BRROconventionals %>% 
  dplyr::select(FDT_STA_ID, FDT_SPG_CODE, FDT_DATE_TIME, FDT_TEMP_CELCIUS, FDT_FIELD_PH, DO_mg_L) %>% 
  bind_rows(
    dplyr::select(BRROregionInfo$windowInfo, FDT_STA_ID = Fdt_Sta_Id, FDT_SPG_CODE = Fdt_Spg_Code, FDT_DATE_TIME = Fdt_Date_Time, FDT_TEMP_CELCIUS = Fdt_Temp_Celcius, FDT_FIELD_PH = Fdt_Field_Ph, DO_mg_L = Fdt_Do_Optical, FDT_SPECIFIC_CONDUCTANCE = Fdt_Specific_Conductance)) %>% 
  filter(FDT_SPG_CODE != "QA") %>% 
  mutate(Year = year(FDT_DATE_TIME)) %>%  
 group_by(FDT_STA_ID, Year) %>% 
  mutate(`Sample n`= n(),
         `Temp NAs`= count_na(FDT_TEMP_CELCIUS),
         `pH NAs` = count_na(FDT_FIELD_PH),
         `DO NAs` = count_na(DO_mg_L),
         `SpC NAs` = count_na(FDT_SPECIFIC_CONDUCTANCE)) %>%
 group_by(FDT_STA_ID, Year) %>% 
  summarise(`Sample n` = n(), #only counting unique rows of sta ID, div by year
            `SPG codes` = paste(unique(FDT_SPG_CODE),  collapse = ' | '),
            `SPG codes First` = as.factor(unique(FDT_SPG_CODE)[1]), # keep this first one for mapping purposes
            `Temp NAs`= as.numeric(unique(`Temp NAs`)[1]), #just stealing the first value of the na count
            `pH NAs` = as.numeric(unique(`pH NAs`)[1]),
            `DO NAs` = as.numeric(unique(`DO NAs`)[1]),
            `SpC NAs` = as.numeric(unique(`SpC NAs`)[1])) %>%
  mutate(IR2022 = case_when(Year %in% c(2015:2020) ~ 'IR 2022',
                                       TRUE ~ as.character(NA)),#from orig, makes identifiers for your counts
         IR2024 = case_when(Year %in% c(2017:2022) ~ 'IR 2024',
                                       TRUE ~ as.character(NA)),
         IR2026 = case_when(Year %in% c(2019:2024) ~ 'IR 2026',
                                       TRUE ~ as.character(NA)),
         IR2028 = case_when(Year %in% c(2021:2026) ~ 'IR 2028',
                                       TRUE ~ as.character(NA))) %>% 
  group_by(FDT_STA_ID, IR2022 ) %>% 
  mutate(`IR2022 Sample n` = case_when(IR2022 == 'IR 2022' ~ sum(`Sample n`))) %>% 
     ungroup() %>% group_by(FDT_STA_ID, IR2024 ) %>% 
  mutate(`IR2024 Sample n` = case_when(IR2024 == 'IR 2024' ~ sum(`Sample n`)), 
         `IR2024 Temp NAs` = case_when(IR2024 == 'IR 2024' ~ sum(`Temp NAs`)), #well this is not elegant
         `IR2024 pH NAs` = case_when(IR2024 == 'IR 2024' ~ sum(`pH NAs`)),
         `IR2024 DO NAs` = case_when(IR2024 == 'IR 2024' ~ sum(`DO NAs`)),
         `IR2024 SpC NAs` = case_when(IR2024 == 'IR 2024' ~ sum(`SpC NAs`))) %>% 
      ungroup() %>%  group_by(FDT_STA_ID, IR2026 ) %>% 
  mutate(`IR2026 Sample n` = case_when(IR2026 == 'IR 2026' ~ sum(`Sample n`)),
         `IR2026 Temp NAs` = case_when(IR2026 == 'IR 2026' ~ sum(`Temp NAs`)),
         `IR2026 pH NAs` = case_when(IR2026 == 'IR 2026' ~ sum(`pH NAs`)),
         `IR2026 DO NAs` = case_when(IR2026 == 'IR 2026' ~ sum(`DO NAs`)),
         `IR2026 SpC NAs` = case_when(IR2026 == 'IR 2026' ~ sum(`SpC NAs`))) %>% 
      ungroup() %>%  group_by(FDT_STA_ID, IR2028 ) %>% 
   mutate(`IR2028 Sample n` = case_when(IR2028 == 'IR 2028' ~ sum(`Sample n`)),
          `IR2028 Temp NAs` = case_when(IR2028 == 'IR 2028' ~ sum(`Temp NAs`)),
          `IR2028 pH NAs` = case_when(IR2028 == 'IR 2028' ~ sum(`pH NAs`)),
          `IR2028 DO NAs` = case_when(IR2028 == 'IR 2028' ~ sum(`DO NAs`)),
          `IR2028 SpC NAs` = case_when(IR2028 == 'IR 2028' ~ sum(`SpC NAs`))) %>% 
  ungroup() %>% 
  dplyr::select(-c(IR2022, IR2024, IR2026, IR2028)) 
 
#a table just showing sample n's and param percent reporting by IR window
ParamSamplePerc <- ParamSampleInfo %>%
  mutate(IR24Temp = (`IR2024 Sample n` - `IR2024 Temp NAs`)/ `IR2024 Sample n` * 100,
         IR24pH = (`IR2024 Sample n` - `IR2024 pH NAs`)/ `IR2024 Sample n`* 100,
         IR24DO = (`IR2024 Sample n` - `IR2024 DO NAs`)/ `IR2024 Sample n`* 100,
         IR24SpC = (`IR2024 Sample n` - `IR2024 SpC NAs`)/ `IR2024 Sample n`* 100,
         
         IR26Temp = (`IR2026 Sample n` - `IR2026 Temp NAs`)/ `IR2026 Sample n`* 100,
         IR26pH = (`IR2026 Sample n` - `IR2026 Temp NAs`)/ `IR2026 Sample n`* 100,
         IR26DO = (`IR2026 Sample n` - `IR2026 Temp NAs`)/ `IR2026 Sample n`* 100,
         IR26SpC = (`IR2026 Sample n` - `IR2026 Temp NAs`)/ `IR2026 Sample n`* 100,
         
         IR28Temp = (`IR2028 Sample n` - `IR2028 Temp NAs`)/ `IR2028 Sample n`* 100,
         IR28pH = (`IR2028 Sample n` - `IR2028 Temp NAs`)/ `IR2028 Sample n`* 100,
         IR28DO = (`IR2028 Sample n` - `IR2028 Temp NAs`)/ `IR2028 Sample n`* 100,
         IR28SpC = (`IR2028 Sample n` - `IR2028 Temp NAs`)/ `IR2028 Sample n`* 100) %>%
   mutate(flag = if_else(c(IR24Temp:IR28SpC) == 100.0000, "ok", "FLAG")) %>% #right now get 100% flag because no station reporting 100% SpC for every window
    dplyr::select(-c(`Temp NAs`, `pH NAs`, `DO NAs`, `SpC NAs`,
                    `IR2024 Temp NAs`, `IR2024 pH NAs`, `IR2024 DO NAs`, `IR2024 SpC NAs`,
                    `IR2026 Temp NAs`, `IR2026 pH NAs`, `IR2026 DO NAs`, `IR2026 SpC NAs`,
                    `IR2028 Temp NAs`, `IR2028 pH NAs`, `IR2028 DO NAs`, `IR2028 SpC NAs`)) 
  
write.csv(ParamSamplePerc, "SampleN_byIRandParam.csv")
   
```



the part where I accidentally developed a sample fail finder, fun!
```{r}
#NUMBER in TABLE tells you if there is an NA for that parameter, i.e. if it is missing from that station's data
#flag tells you if missing data is uneven across the 3 params, i.e. more data for one param than for others
#subset gives you just flagged stations to check out

summarizeByParameter2 <- function(x){
    x %>%
      select(FDT_STA_ID, FDT_DATE_TIME, FDT_FIELD_PH, FDT_TEMP_CELCIUS, DO_mg_L) %>%
      mutate(Year = year(FDT_DATE_TIME)) %>% 
      group_by(FDT_STA_ID, Year) %>%
      summarise_all(funs(sum(is.na(.)))) %>%
        mutate(flag = ifelse(FDT_FIELD_PH == FDT_TEMP_CELCIUS & FDT_FIELD_PH == DO_mg_L & FDT_TEMP_CELCIUS == DO_mg_L, "ok", "flag")) %>%
        subset(flag == "flag")
}
#extra summ sample count! gives you a denominator for your percentage -- ALL THE STATIONS for 2015-2020 
#filter by IR22 window aka 2015-2020, summ param flag
#do INVIDV param flag

summarizeByParameter2(BRROconventionals) 

ParamNAs <- function(x) {
    x %>%    
        select(FDT_STA_ID, FDT_DATE_TIME, FDT_FIELD_PH, FDT_TEMP_CELCIUS, DO_mg_L) %>%
        group_by(FDT_STA_ID) %>%
        summarise_all(funs(sum(is.na(.)))) 
}

ParamNAs(BRROconventionals)
```



